A Novel Model-Free Learning Approach for Dynamic Target Tracking Problem and its Validation using Virtual Robot Experimentation Platform

### 2020-07-01 paperMIC2020/paperIEEE-MIC2020-V1.tex

Over the past years mobile robots has been used in several applications in commercial and military sectors such as surveillance, search and rescue missions,coverage optimization, cooperative localization and dynamic target tracking tasks \cite{kolling2006},\cite{Encarnacao2001},\cite{Ju2001}.  In all of these mentioned applications a fleet of robot i.e agents interact with each other to achieve a certain goal. Leader-Follower or dynamic target tracking problem has recieved an extensive amount of study and research in the world of cooperative control theory due to it's wide promising applications such as search and rescure missions, wildlife monitoring and survillance to name a few . In a typical leader follower formation a number of robots referred to as followers apply local control actions to follow leader's robots in a specific predefined path such as \hl {cyclic, circular motion and time varying communication topologies.} \hl {limitations of other methods} many control methods were proposed however they have had the following limitations:
\\(1) a static leader/target is used.
\\(2) the leade/target's location or dynamic model is predetermined.  
\\(3) expensive hardware platforms are used to achieve the mobile target tracking.

>>>>

Over the past years mobile robots has been used in several applications in commercial and military sectors such as surveillance, search and rescue missions,coverage optimization, cooperative localization and dynamic target tracking tasks to name a few \cite{kolling2006},\cite{Encarnacao2001},\cite{Ju2001}.  In all of these mentioned applications a fleet of robot i.e agents interact with each other to achieve a certain goal. Leader-Follower or dynamic target tracking problem has recieved an extensive amount of study and research in the world of cooperative control theory due to it's promising applications in research and industry. In a typical target tracking formation a number of robots referred to as followers apply local control actions to follow a target in a specific predefined path such as \hl {cyclic, circular motion and time varying communication topologies.} many control methods were proposed however they have had the following limitations:
\\(1) a static leader/target is used.
\\(2) the leade/target's location or dynamic model is predetermined.  
\\(3) expensive hardware platforms are used to achieve the mobile target tracking.
